Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Edit the abstract
Minor edits only. It was very good to begin. Just cleared up some
wording.

\begin{summary}
We present a new methodology to compute the gravitational fields generated by
any tesseroid whose density varies continuously in depth, i.e. a forward
gravity model in spherical coordinates for varying densities on the radial
direction.
It numerical approximates these gravitational fields through the
Gauss-Legendre Quadrature along with two discretization algorithms that
increase its accuracy by subdividing the tesseroid into smaller ones.
The first one is a preexisting adaptive discretization algorithm that reduces
the errors due to the distance between the tesseroid and the computation
point.
While the second one  is a new density-based discretization algorithm that
decreases the errors introduced by the variation of the density function.
The amount of discretizations made by each algorithm is indirectly controlled
by two predefined scalar values: the distance-size ratio $D$ for the former
and the delta ratio $\delta$ for the latter.
We have also obtained analytical solutions for a spherical shell with variable
density and compared them with the results of the numerical model in case of a
linear and an exponential density function.
These comparisons allowed to obtain default values for the distance-size and
the delta ratio in order to guarantee the accuracy of the forward model.
The resulting optimal values of $D$ for the gravity potential, the components
of its gradient and the Marussi tensor components are 1, 2 and 8,
respectively.
While a $\delta=0.2$ is needed for the computation of the gravitational
potential and its gradient components and a $\delta=0.01$ must be used for
the Marussi tensor components.
We have finally tested this new methodology by modelling the Neuqu\'en
sedimentary basin, located to the east of the Andes between 32$^\circ$S and
40$^\circ$S latitude, assigning an exponential density variation to it and
computing all the gravitational fields it generates.
\end{summary}

>>>>

\begin{summary}
We present a new methodology to compute the gravitational fields generated by
tesseroids (spherical prisms) whose density varies continuously with depth according to
an arbitrary function.
It approximates the gravitational fields through the Gauss-Legendre Quadrature along
with two discretization algorithms that automatically control its accuracy by adaptively
dividing the tesseroid into smaller ones.
The first one is a preexisting adaptive discretization algorithm that reduces
the errors due to the distance between the tesseroid and the computation
point.
The second is a new density-based discretization algorithm that
decreases the errors introduced by the variation of the density function with depth.
The amount of divisions made by each algorithm is indirectly controlled
by two parameters: the distance-size ratio and the delta ratio.
We have obtained analytical solutions for a spherical shell with radially variable
density and compared them to the results of the numerical model for linear and
exponential density functions.
These comparisons allowed us to obtain optimum values for the distance-size and
delta ratios that yield an accuracy of 0.1\% of the analytical solutions.
The resulting optimal values of distance-size ratio for the gravitational potential, its
gradient, and Marussi tensor are 1, 2 and 8, respectively.
A delta ratio of 0.2 is needed for the computation of the gravitational potential and
its gradient components, while a value of 0.01 must be used for the Marussi tensor
components.
Lastly, we apply this new methodology to model the Neuqu\'en Basin, a foreland basin in
Argentina with a maximum depth of over 5000 m, using an exponential density function.
\end{summary}
